### 2013-11-01 paper/main.tex
added work on talk for NS lab meeting

@@

>>>>

The second issue is that directly modeling the p values, say via non-parametric methods, without taking account of their precision, 
can lead to unrealistic distributions being fitted. Put another way, because z scores are the result of adding noise to some
distribution, the range of distributions they can take is limited Using entirely non-parametric methods loses this information.
The solution is to model beta hat as a convolution of some distribution g and an error component.

@@

Efron (2008) states ``most of the z-values near zero come from null genes"
His main aim in making this assumption is to estimate an empirical null though (not assume N(0,1) for the null)
rather than to impose identifiability.

By modeling the z scores directly under the alternative, rather than the z scores as being the truth plus noise,
maybe that is what is most problematic? Because the resulting distribution of z scores is just not possible.

Note that \cite{muralidharan:2012} models $z$ scores as something plus noise under both $H_0$ and $H_1$, which
avoids this problem. (DOes the same maybe apply to modeling beta, rather than z scores, when the errors vary?)

Rice and Spiegelhalter - BRCA data?
